Distributed lag effects of smoke on cardiovascular disease in persons over 65

### 2017-11-28 r_scripts/analysis/oregon_cvd_dl_over65_results.Rmd
tested out function.
figured out fit loop. Finalizing results tomorrow.

Import CVD data.

@@

# read in all the files in to a list
outcome_df_list <- casecross_order %>%  
  purrr::map(~read_csv(paste0(health_path, .)))

# name dataframes
names(outcome_df_list) <- file_names

@@

```{r distributed lag functions}

# fit function
dl_fit <- function(data, pm_df, temp_df){
  # i want to remove this part eventually ------
  # limit to complete cases
  complete_data <- data %>% 
    # filter to complete case for smoke
    filter(!is.na(geo_smk_pm_lag7_zip))

@@

    # find minimum aic
    pm_df_aic <- data.frame(pm_df, mod_aic)
    min_df_aic <- subset(pm_df_aic, mod_aic == min(mod_aic))
    return(min_df_aic)
  } # end fit option

dl_fit(data = hf65, pm_df = c(3:5), temp_df=2)

# custom distributed lag function 
distributed_lag <- function(data, pm_df, temp_df, cumulative=T){
  # i want to remove this part eventually ------
  # limit to complete cases
  complete_data <- data %>% 
    # filter to complete case for smoke
    filter(!is.na(geo_smk_pm_lag7_zip))

@@

@@

cumulative <- distributed_lag(hf65, pm_df = 4, temp_df = 2, cumulative = T)
cumulative

@@

@@

>>>>

Importing the time-stratified case-crossover dataframes for the cardiovascular endpoints.

@@

# read in all the files in to a list
cvd_over65_list <- casecross_order %>%  
  purrr::map(~read_csv(paste0(health_path, .))) %>% 
  # filter to over 65 group
  purrr::map(~filter(., age >= 65))

# name dataframes
names(cvd_over65_list) <- file_names

@@

```{r custom distributed lag fit function}
# fit function
dl_fit <- function(data, pm_df, temp_df){
  # i want to remove this part eventually ------
  # limit to complete cases
  complete_data <- data %>% 
    # filter to complete case for smoke
    filter(!is.na(geo_smk_pm_lag7_zip))

@@

    # find minimum aic
    pm_df_aic <- data.frame(pm_df, mod_aic)
    min_df_aic <- subset(pm_df_aic, mod_aic == min(mod_aic))
    return(min_df_aic)
  } # end fit option
```

```{r custom distributed lag function}
# custom distributed lag function 
distributed_lag <- function(data, pm_df, temp_df, cumulative=T){
  # i want to remove this part eventually ------
  # limit to complete cases
  complete_data <- data %>% 
    # filter to complete case for smoke
    filter(!is.na(geo_smk_pm_lag7_zip))

@@

## Finding smoke distributed lag fit based on AIC

This chunk of code uses the dl_fit function I created to find the degrees of freedom for the natural spline that has the lowest AIC for degrees of freem from 2 to 5 for the smoke lag function. I set temperature degrees of freedom to 2.

```{r smk aic fit}
fit_df <- cvd_over65_list %>% 
  purrr::map_df(~dl_fit(., pm_df = c(2:5), temp_df =2)) %>% 
  cbind(names(cvd_over65_list), .)

# add degrees of freedom as a slot to the outcomes list
degfreedom_list <- as.list(fit_df$pm_df)
```

## Distributed Lag Cumulative Effect

Calculating the cumulative effect sequentially (0, 0+1, 0+1+2,....)

```{r cumulative effect smooth}
cumulative_cvd <- purrr::map2(.x = cvd_over65_list, .y = degfreedom_list, 
  ~distributed_lag(data = .x, pm_df = .y, temp_df = 2, cumulative = T)) %>% 
  plyr::rbind.fill() %>% 
  bind_cols(., data_frame(rep(outcome_names, each=8))) %>% 
  rename(outcome_names = `rep(outcome_names, each = 8)`) %>% 
  select(outcome_names, type, time, estimate, lower95, upper95) %>% 
  # preserve order of names
  mutate(outcome_names = parse_factor(outcome_names, levels = outcome_names))
```

@@

cumulative <- distributed_lag(hf65, pm_df = 2, temp_df = 2, cumulative = T)
cumulative

@@

dl_plot
```

@@

check <- mi65 %>% filter(personkey == 1782923) %>% 
  select(personkey, outcome, dx1, date, fromdate)
